Synthesising Complex Termination Arguments

### 2014-06-16 papers/termination/paper.tex
Change multiphase ranking function
changed motivation

@@

@@

Every execution of the program in Figure~\ref{} can be partitioned into two phases: in the first phase $y$ increases
until it is positive (in this phase $q$ may increase), whereas in the second $q$ decreases until the loop condition is violated. 
\cite{DBLP:conf/tacas/LeikeH14} proposes using a linear ranking template in order to obtain a ranking function that proceeds
through a fixed number of phases in the program execution. Each phase is ranked by a linear function, and ends when this function becomes non-positive.
However, when considering the bit-vector semantics, this program does not terminate.

@@

%% t3 is "If x >= y, then x' >= y'" where x' is the next value of x.  This can be interpreted as "if the 'else' branch of the if is taken once, it is taken forever", which can be seen by induction.
%% t2 is z -- this is probably the sickest part.  In the 'else' branch, z just decreases.  In the 'then' branch, we get:

%% y > x
%% y' = z
%% x' = nondet()
%% z' = x' - 1

%% Let's consider 2 cases:

%% case z' >= z, then:
%%   x' - 1 >= z, so
%%   x' - 1 >= y', so
%%   x' > y',
%%   so (x < y) has decreased, i.e. we will reamain in the 'else' branch forever and
%% case z' < z, then:
%%   z has decreased.

>>>>

% The main advantage of our approach is its unitary nature. We do not require any initial assumption regarding the form of the termination  
% argument, as this does not influence our search process. We identify the factors influencing the performance of our design and 
% show that these factors are independent on the linearity of the ranking function or the number of lexicographic components...

@@

The program in Figure~\ref{} is taken from \cite{DBLP:conf/tacas/CookSZ13}, where
$m$ and $x$ start as any integers with $m$ positive. If $x$ is greater than
$m$, $x$ is set to 0. Otherwise, $x$ increases until it equals $m$, upon which
the loop terminates. While a disjunctive well-founded termination argument does exist for the loop, 
e.g. ($x < oldx$ and $0 \leq oldx$) or ($m-x < oldm-oldx$ and $0 \leq oldm-oldx$), the loop does not 
terminate under the bit-vector semantics. The reason is ..

@@

In Figure~\ref{}, every execution of the program can be partitioned into two phases: in the first phase $y$ increases
until it is positive (in this phase $q$ may increase), whereas in the second $q$ decreases until the loop condition is violated. 
This example was presented in \cite{DBLP:conf/tacas/LeikeH14}, where the authors make use of a template for obtaining a ranking function that proceeds
through a fixed number of phases in the program execution. Each phase is ranked by a linear function, and ends when this function becomes non-positive.
However, when considering the bit-vector semantics, this program does not terminate as..

@@
